PK object batch mode trial

### 2023-06-27 data-raw/batchMode_trial_gpm.Rmd
Expanded the time interpolation. Added conditional labelling legend order.

```{r plotting_method}
# Experimenting with what works with my_ndf
# 
my_ndf <- my_pk$data

my_ndf %>%
  filter(Chemical %in% "DTXSID0020442", Species %in% "rat") %>%
  mutate(Dose = factor(Dose),
         Reference = factor(Reference),
         Detect_int = as.character(Detect)
         ) %>%
  ggplot(aes(
    x = Time_trans,
    y = Conc_trans,
    color = Dose,
    shape = Reference
  )) +
  geom_point(aes(
    fill = Dose,
    alpha = Detect_int
  )) +
  geom_point() +
  scale_shape_manual(values = 21:25) +
  scale_alpha_manual(values = c("FALSE" = 0, "TRUE" = 1),
                     breaks = c("TRUE", "FALSE"),
                     name = "Detect") +
  guides(shape = guide_legend(override.aes = list(fill = "black")),
         alpha = guide_legend(override.aes = list(alpha = 1,
                                                  fill = c("black", "white"),
                                                  color = "black",
                                                  shape = 21))) +
  facet_grid(rows = vars(Detect), # This is just for illustrative purposes, this would be Routes
             cols = vars(Route)) +
  theme_bw()
# Need to find a way to make this vectorized...
# probably within a mutate and map function

req_vars <- c("Time",
              "Time.Units",
              "Dose",
              "Route",
              "Media",
              "Reference",
              "Conc",
              "Conc_SD",
              "Value",
              "Value.Units",
              "Detect", "exclude")

trans_vars <- c("Time_trans",
                "Time_trans.Units",
                "Conc_trans",
                "Conc_trans.Units")

my_ndf %>%
  dplyr::select(Chemical, Species,
                dplyr::all_of(req_vars),
                dplyr::any_of(trans_vars)) -> my_ndf

# Time interpolation
my_ndf %>% uncount(1) %>% 
  group_by(Dose, Route, Media) %>%
  mutate(Time_trans = (max(Time)/(n() - 1))*(row_number() - 1)) %>%
  View()

devtools::load_all()
my_plot <- plot(my_pk, use_scale_conc = FALSE)

>>>>

```{r plotting_method}

devtools::load_all()
my_plot <- plot(my_pk, use_scale_conc = FALSE)
plot(my_pk, use_scale_conc = TRUE,
     method = "L-BFGS-B",
     print_out = TRUE)

# This is printable into a one file, multipage pdf
pdf(file = "C:/Users/GPADILLA/OneDrive - Environmental Protection Agency (EPA)/Profile/Documents/Code Notes/plotMethod_OnefileTest.pdf",
    width = 10,
    height = 8)
plot(my_pk, use_scale_conc = TRUE,
     method = "L-BFGS-B",
     print_out = TRUE)
dev.off()
